Self Regulation Ontology Retest Data Report

### 2017-04-06 SRO_Report.Rmd
changed to new retest release

### Load time 2 data 
```{r}
retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables.csv')

retest_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables_noDDM.csv')

retest_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/meaningful_variables_EZ.csv')

@@

So what variables show a non-negligible effect of time and in what direction?

```{r warning=FALSE, message=FALSE}
ggplot_build(icc_df %>%
               ggplot(aes(eta_sq, fill=task)) +
               geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
  mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
  get_labels(.,icc_df, "eta_sq", "task") %>%
  prettify_label(.) %>%
  filter(bin != 1 & bin !=2 & !is.na(label)) %>%
  select(label)

anyNA("NA") 
```

@@

Some variables (`r neg_icc_vars$dv`) have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. That is, ICC would be negative if the ...

@@

Ties?

"The group of zero values for the ICC may be that the ICC is more of a measure of consistency than the Spearman/Pearson measures of rank order similarity.  Or it could be the ICC calculation is off in some way. It would be worth focusing on five of these unusual cases (where the ICC is zero but the Pearson/Spearman is large) and calculate the ICC using other formulas.  Generally the Spearman and Pearson differ when there are ties.""

```{r}
ties_df <- data.frame(unique_entries = rep(NA, length(numeric_cols)), 
                     transformed = rep(NA, length(numeric_cols)))

@@

# Completion dates

Is a subject more/less consistent depending on how much time has passed in between?

How do you aggregate all this information to decide on what is a good measure?

Do any of these quantifications of reliability relate to number of items (e.g. surveys with fewer items are more or less reliable - easier to remember or noisier?)

--------------------
One reason why it's difficult to get a sense of what is going on in this paper other than just saying that questionnaires have higher reliability than tasks is because there are too many measures. While a discussion on why some measures are more reliable than others might help with this and in building readers' intuitions about better ways to measure these constructs the paper might have a larger impact andbe eeasier to digest with more of an organizational structure, parsing these variables. 
On the one hand this could be a little contrary to our general theory blind approach to these measures but on the other hand it could also help us reinforce the terminology we are converging on with the analyses of the factor structure of these data. Because at the end of the day this paper would be most useful if it can make prescriptive recommendations on which tasks to use and reduce the utilitization of non-reliable measures.

>>>>

### Load time 2 data 
```{r}
retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables.csv')

retest_data2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables_noDDM.csv')

retest_data3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/meaningful_variables_EZ.csv')

@@

So what variables show a non-negligible effect of time and in what direction? (sorted by increasing partial $\eta^2$)

```{r warning=FALSE, message=FALSE}
time_effect_vars = ggplot_build(icc_df %>%
               ggplot(aes(eta_sq, fill=task)) +
               geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
  mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
  get_labels(.,icc_df, "eta_sq", "task") %>%
  prettify_label(.) %>%
  filter(bin != 1 & bin !=2 & label != "NA") %>%
  select(label, task) %>%
  separate(label,into=c(as.character(1:27)),sep = "</br>") %>%
  gather(key, value, -task) %>%
  select(value, task) %>%
  na.omit()

time_effect_vars$value = gsub("\"", "", time_effect_vars$value)
time_effect_vars
```

Here is a scatter plot of these variables but I'm not including it in the report for now because it is too large and because I want to get back to this once I refit the hddm's for retest participants only.

```{r warning=FALSE, message=FALSE, fig.height=72, eval=FALSE}
tmp = data.frame()

for(i in 1:nrow(time_effect_vars)){
  tmp = rbind(tmp, match_t1_t2(time_effect_vars$value[i]))
}
rm(time_effect_vars)

tmp = tmp %>%
  inner_join(icc_df[,c("dv", "eta_sq")],by="dv")

tmp = tmp %>% 
  mutate(dv = factor(dv, levels = unique(tmp$dv[order(tmp$eta_sq)])))

ggplotly(tmp %>%
  spread(time, score) %>%
  ggplot(aes(`1`, `2`))+
  geom_point()+
  theme_bw()+
  facet_wrap(~dv, scales='free', labeller = label_wrap_gen())+
  geom_abline(intercept = 0, slope=1))
```

@@

Some variables (`r neg_icc_vars$dv`) have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$.

@@

```{r echo=FALSE, eval=FALSE}
# Ties?
# 
# "The group of zero values for the ICC may be that the ICC is more of a measure of consistency than the Spearman/Pearson measures of rank order similarity.  Or it could be the ICC calculation is off in some way. It would be worth focusing on five of these unusual cases (where the ICC is zero but the Pearson/Spearman is large) and calculate the ICC using other formulas.  Generally the Spearman and Pearson differ when there are ties.""

ties_df <- data.frame(unique_entries = rep(NA, length(numeric_cols)), 
                     transformed = rep(NA, length(numeric_cols)))

@@
